Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-17 article/ms.tex
additional discussion points

\item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419. however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such. However, since only 113 out of \LamostGiants stars

>>>>

\item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419. however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such. Only 113 out of \LamostGiants \ stars were found to be good candidates for enhanced K and reduced Mg. Likely not products of the same process as acted in NGC 2419, but possibly? Main implications: searched \LamostGiants \ stars, but didn't find any that we could say 'yeah that looks like it could have came from the same process that caused NGC 2419's signiature'.

\item What does this abundance imply about pollution mechanisms? depends whether we decide that our identified stars were produced by the same process or not. IF they weren't produced by the same process, then this is further evidence that the event/object was unique to old globular clusters. If however they WERE produced by the same process, but just weren't as polluted (the primordial material was made up of a lower fraction of anomalously enriched material), then the implications are a bit weird. We found stars across a large range of metalicities. Diferent formation times is also implied by metalicity.

\item spread in Logg and Teff: the fact that we see stars across a range of Teff and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.

\item working hypothesis (John, Tout): We decouple the Mg and the K. A SAGB binary with a smaller companion. the SAGB produces K, which then accretes to the companion. the companion will evolve long after the SAGB explodes, then will either (depending on mass/temperature) undergo hot bottom burning or it won't. If it does? undergo hot bottom burning then Na will be produced. If it doesn't? undergo hot bottom burning then Na won't be produced. other predictions: O shouldn't? be be there, nor should C or N as they get turned into Na. This scenario is plausible to happen in the MW disk, throughout an extended period of time, therefore being consistent with the spread in metalicities that we see. Look at iliadis 2017 to see some other implications of hot bottom burning in AGB (low temperature) star and SAGB (high temp) burning.

\item We're not allowed to have a single big event in NGC 2419 and then clumps of material floating round the galaxy and occasionally forming a star. one good reason: its really distant form the galaxy. thus our K enhancements must source from a star inside the galaxy, NOT a globular cluster. this raises some interesting issues. If the source of our K enhancements is the same as NGC 2419, where we had Mg depletions that then were later covered up/ reduced in magnitude in the case of our disk stars, then the big question i'd want answered is: So we have this thing that only occurs in 2419... and the MW disk... throughout the life of the MW disk... but not in any other globular clusters. seems a bit picky...

\item novae: the mass budged problem is much worse for NGC 2419 than \cite{iliadis2016} made it appear, and is very unlikely to be responsible for the phenomena. finding even more K enhanced stars in the MW doesn't change this.
